Network Configuration Synthesis with Abstract Topologies

### 2016-11-14 paper/abstraction/paper.tex
add concrete templates

@@

To simplify network configuration, operators are adopting a template-based approach~\cite{hatch,thwack}. Instead of authoring a configuration per router, operators author a template per role.
%
A {\em role} is a specific function that is served by one or more routers.
%\footnote{If a role is played by devices from multiple vendors, there is one template per role-vendor combination because templates use vendor configuration languages.}
%
The network in Figure~\ref{fig:example} might have five roles: spine, global aggregator, global ToR, local aggregator, and local ToR.
%
Templates have parameters for various aspects of the configuration (\EG, neighbor list) and are compiled to device configurations by instantiating the parameters using the network topology and a database of network information.

@@

\para{Template Generation}

@@

Second, \sysname checks if the fault-tolerance policy can be met by considering the joint impact of the abstract topology and routing policy. Joint analysis is needed, because connectivity depends on both: traffic will not flow along
valid topological paths if the routing policy disallows it.

We develop a sound analysis based on computing the minimum
number of edge-disjoint, policy-compliant paths between pairs of nodes
over abstract topologies. If this number is less
than the desired fault-tolerance level for a pair of nodes, \sysname declares that the
policy cannot be met.
\ryan{Possibly cut here}
More specifically,
for each abstract role in the network, our analysis will learn facts about the
number of disjoint paths to routers in that role.  For example,
the fact $A_{S}(2,3)$ states that for \emph{all} groups of 2 nodes
in the $S$ (Spine) role, there are 6 disjoint paths to the group---3
for each of the 2 nodes. A fact such as $S_{S}(2,3)$, states that
\emph{some} group of 2 nodes has the property as opposed to all.
More generally, there is one quantifier ($A$ for all groups
and $S$ for exists a group).  When nodes are nested within pods,
there is one quantifier for each level of the hierarchy, so
$S_P S_{TG} (i,j)$ means that for some pod from the $P$ group of pods
and for some nodes in the $TG$ role within that pod, there exists a
group of $i$ nodes with $j$ paths to each node in the group.

\ryan{Possibly cut here}
As an example, suppose we want to compute the number of of disjoint paths
between any
global ToR and spine router in Figure~\ref{fig:example3}.
%This can be used as a lightweight verification tool to detect certain classes of configuration bugs. For example, since the network is performing prefix summarization at the border of the datacenter, we might introduce a black hole after enough failures occur to disconnect a tor from a spine router.
The analysis begins with the fact
$S_P S_{TG} (1,1)$---there is some group of
nodes of size 1 in the $TG$ role in some pod $P$ such that any initial
node in the $TG$ role has 1 disjoint path to it (and all such paths are
edge-disjoint). Since the abstract topology specifies that each node in
the $TG$ role is in
a full mesh with nodes in the $AG$ role within any given pod, we
infer the fact $S_P A_{AG}(e1,1)$. This says that
any group of nodes of size e1 in the $AG$ role is reachable with at
least 1 path to each such node from any initial node in
the $TG$ role.
%
After one more step, the analysis will learn a fact of the form $A_{S}(1,1)$, which means that any single spine node is reachable via a single disjoint path from any initial global ToR node
In fact, due the the valley-free routing constraint, a single path is
the worst-case fault-tolerance level for the concrete network from
Figure~\ref{fig:example2}.

If \sysname finds that the fault-tolerance policy can be met, it generates templates for the abstract topology.  Per-device BGP configurations can in turn be generated from the templates
using information in the concrete topology. To ensure the process is sound,
\sysname checks that the given concrete topology is an instance of the abstract topology.

>>>>

\begin{figure}[t!]
  \centering
  \includegraphics[width=1.02\columnwidth]{figures/templates}
  \caption{Example of a small part of a router template for the datacenter spine role.}
  \label{fig:example2}
  \vspace{-1em}
\end{figure}

@@

To simplify network configuration, operators are adopting a template-based approach~\cite{hatch,thwack}. Instead of authoring a configuration per router, operators author a template per role.
%
A {\em role} is a specific function that is served by one or more routers.
%\footnote{If a role is played by devices from multiple vendors, there is one template per role-vendor combination because templates use vendor configuration languages.}
%
The network in Figure~\ref{fig:example} might have five roles: spine, global aggregator, global ToR, local aggregator, and local ToR.
%
Templates have parameters for various aspects of the configuration (\EG, neighbor list) and are compiled to device configurations by instantiating the parameters using the network topology and a database of network information.
\ryan{TODO: discuss figure}

@@

\para{Synthesis}

@@

Second, \sysname checks if the fault-tolerance policy can be met by considering the joint impact of the abstract topology and routing policy. Joint analysis is needed, because connectivity depends on both: traffic will not flow along
valid topological paths if the routing policy disallows it.
%
We develop a sound analysis based on computing the minimum
number of edge-disjoint, policy-compliant paths between pairs of nodes
over abstract topologies. If this number is less
than the desired fault-tolerance level for a pair of nodes, \sysname declares that the
policy cannot be met.
%\ryan{Possibly cut here}
%More specifically,
%for each abstract role in the network, our analysis will learn facts about the
%number of disjoint paths to routers in that role.  For example,
%the fact $A_{S}(2,3)$ states that for \emph{all} groups of 2 nodes
%in the $S$ (Spine) role, there are 6 disjoint paths to the group---3
%for each of the 2 nodes. A fact such as $S_{S}(2,3)$, states that
%\emph{some} group of 2 nodes has the property as opposed to all.
%More generally, there is one quantifier ($A$ for all groups
%and $S$ for exists a group).  When nodes are nested within pods,
%there is one quantifier for each level of the hierarchy, so
%$S_P S_{TG} (i,j)$ means that for some pod from the $P$ group of pods
%and for some nodes in the $TG$ role within that pod, there exists a
%group of $i$ nodes with $j$ paths to each node in the group.

%\ryan{Possibly cut here}
%As an example, suppose we want to compute the number of of disjoint paths between any global ToR and spine router in Figure~\ref{fig:example3}.
%The analysis begins with the fact
%$S_P S_{TG} (1,1)$---there is some group of
%nodes of size 1 in the $TG$ role in some pod $P$ such that any initial
%node in the $TG$ role has 1 disjoint path to it (and all such paths are
%edge-disjoint). Since the abstract topology specifies that each node in
%the $TG$ role is in
%a full mesh with nodes in the $AG$ role within any given pod, we
%infer the fact $S_P A_{AG}(e1,1)$. This says that
%any group of nodes of size e1 in the $AG$ role is reachable with at
%least 1 path to each such node from any initial node in
%the $TG$ role.
%
%After one more step, the analysis will learn a fact of the form $A_{S}(1,1)$, which means that any single spine node is reachable via a single disjoint path from any initial global ToR node
%In fact, due the the valley-free routing constraint, a single path is
%the worst-case fault-tolerance level for the concrete network from
%Figure~\ref{fig:example2}.

If \sysname determines that the fault-tolerance policy can be met, it generates templates for the abstract topology.  Per-device BGP configurations can in turn be generated from the templates
using information in the concrete topology. To ensure the process is sound,
\sysname checks that the given concrete topology is an instance of the abstract topology.
